Incentivizing Exploration with Unbiased History

### 2018-10-23 3level.tex
refactoring

\section{3-level Adaptive Policy}
\label{sec:3level}
Now we demonstrate how to design a e-level policy to incentivize
adaptive exploration and improve on the $O(T^{2/3})$ regret rate. In
\Cref{sec:llevel}, we will show how to extend this idea to achieve a
regret rate of $\tilde O(T^{1/2})$. For simplicity, we will focus on
the setting with 2 arms.

The 3-level recommendation policy is constructed as following. Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 = T^{6/7}\log^{-5/7}(T)$. The first level has $S = 2^{10}\log(T)$ groups of agents. Each group runs $T_1$ \ALGG of $T_G$ rounds in parallel. The second level also has $S$ groups of agents. Each group has $T_2$ agents and they observe the history of corresponding group in the first level. All the rest agents are in the third level and they observe the entire history of the first two levels. 
See also Figure \ref{fig:3level} for a graphical view of the information flow.

Here we give some intuition about how the 3-level recommendation policy works. The main idea is to do the exploration more adaptively. In the first level, agents explore both arms. In the second level, agents will pull the best arm when $\mu_1 - \mu_2$ is large ($\tilde{\Omega}(1/\sqrt{T_1})$). Otherwise agents will explore both arms more. In the third level, agents will pull the best arm unless $\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$). In the proof, we need not only the concentration argument as the 2-level recommendation policy, but also the anti-concentration argument to show that agents explore more in the second round if $\mu_1-\mu_2$ is not too big.

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=green!20!white]
 (0,4)--(10,4)--(10,5)--(0,5)--cycle;
 \foreach \x in {0,3,8}
 {
 \filldraw[fill=blue!20!white]
 (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
 \draw[dashed] (\x+1,3)--(5,4);
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
 \draw[dashed] (\x+1,1)--(\x+1,2);
 \draw[dashed] (\x+0.2,1)--(\x+1,2);
 \draw[dashed] (\x+0.6,1)--(\x+1,2);
 \draw[dashed] (\x+1.4,1)--(\x+1,2);
 \draw[dashed] (\x+1.8,1)--(\x+1,2);
 \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
 \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
 \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
 \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
 \node at(\x+1,2.5){$T_2$};
 \node at(\x+1,0.5){$T_1 \cdot \GdT$};
 }
  \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
  \node at (6,1.5){$\cdots$};
  \node at (7,1.5){$\cdots$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \node at(-1,4.5){\textbf{Levle 3}};
  \draw[->] (11,0)--(11,5);
  \node at(11.5,2.5)[ rotate=90]{Time};
\end{tikzpicture}
\caption{3-level Recommendation Policy.}
\label{fig:3level}
\end{figure}

@@

Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
\begin{itemize}
\item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
\swcomment{can we reuse the previous result?}
For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}

For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$. For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]

>>>>

\section{3-level Adaptive Policy}
\label{sec:3level}
Now we demonstrate how to design a 3-level policy to incentivize
adaptive exploration and improve the $O(T^{2/3})$ regret rate to
$\tilde O(T^{4/7})$. In \Cref{sec:llevel}, we will show how to extend
this idea to achieve a regret rate of $\tilde O(T^{1/2})$. For
simplicity, we will focus on the setting with 2 arms.

The policy consists of three phases, each of which corresponds to a
level (see Figure~\ref{fig:3level}).  In the first level, the policy
performs the first round of exploration over the first
$(S\cdot T_1\cdot T_G)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
and $S = 2^{10}\log(T)$. In particular, the policy randomly partitions
the agents into $S$ groups such that each group consists of $T_1$ runs
of \ALGG with $T_G$ rounds. In the second level, the policy performs
further exploration on the next $(S\cdot T_2)$ agents by incorporating
data collected in the first level, where
$T_2 = T^{6/7}\log^{-5/7}(T)$. The agents are again partitioned into
$S$ groups such that the agents in the $s$-th group are shown the same
sub-history from the $s$-th group in the first level. In the third
level, the policy exploits by showing all remaining agents the entire
history from the first two levels.

They main idea for the 3-level policy is that it inserts the second
level as an additional ``checkpoint'' to induce more adaptivity in the
exploration. By running \ALGG in parellel, the first level ensures
that the agents explore both arms. In the second level, agents will
pull the best arm when $\mu_1 - \mu_2$ is large
($\tilde{\Omega}(1/\sqrt{T_1})$). Otherwise agents will explore both
arms more. In the third level, agents will pull the best arm unless
$\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$). In the
proof, we need not only the concentration argument as the 2-level
recommendation policy, but also the anti-concentration argument to
show that agents explore more in the second round if $\mu_1-\mu_2$ is
not too big.

\iffalse
Set $T_1 = T^{4/7}\log^{-1/7}(T)$ and $T_2 =
T^{6/7}\log^{-5/7}(T)$. The first level has $S = 2^{10}\log(T)$ groups
of agents. Each group runs $T_1$ \ALGG of $T_G$ rounds in
parallel. The second level also has $S$ groups of agents. Each group
has $T_2$ agents and they observe the history of corresponding group
in the first level. All the rest agents are in the third level and
they observe the entire history of the first two levels.  See also
Figure \ref{fig:3level} for a graphical view of the information flow.

Here we give some intuition about how the 3-level recommendation
policy works. The main idea is to do the exploration more
adaptively. In the first level, agents explore both arms. In the
second level, agents will pull the best arm when $\mu_1 - \mu_2$ is
large ($\tilde{\Omega}(1/\sqrt{T_1})$). Otherwise agents will explore
both arms more. In the third level, agents will pull the best arm
unless $\mu_1-\mu_2$ is much smaller ($\tilde{O}(1/\sqrt{T_2})$). In
the proof, we need not only the concentration argument as the 2-level
recommendation policy, but also the anti-concentration argument to
show that agents explore more in the second round if $\mu_1-\mu_2$ is
not too big.  \fi

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=green!20!white]
 (0,4)--(10,4)--(10,5)--(0,5)--cycle;
 \foreach \x in {0,3,8}
 {
 \filldraw[fill=blue!20!white]
 (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
 \draw[dashed] (\x+1,3)--(5,4);
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
 \draw[dashed] (\x+1,1)--(\x+1,2);
 \draw[dashed] (\x+0.2,1)--(\x+1,2);
 \draw[dashed] (\x+0.6,1)--(\x+1,2);
 \draw[dashed] (\x+1.4,1)--(\x+1,2);
 \draw[dashed] (\x+1.8,1)--(\x+1,2);
 \draw[dashed] (\x+0.4,0)--(\x+0.4,1); 
 \draw[dashed] (\x+0.8,0)--(\x+0.8,1); 
 \draw[dashed] (\x+1.2,0)--(\x+1.2,1); 
 \draw[dashed] (\x+1.6,0)--(\x+1.6,1);  
 \node at(\x+1,2.5){$T_2$};
 \node at(\x+1,0.5){$T_1 \cdot \GdT$};
 }
  \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
  \node at (6,1.5){$\cdots$};
  \node at (7,1.5){$\cdots$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \node at(-1,4.5){\textbf{Levle 3}};
  \draw[->] (11,0)--(11,5);
  \node at(11.5,2.5)[ rotate=90]{Time};
\end{tikzpicture}
\caption{3-level Policy.}
\label{fig:3level}
\end{figure}
\swcomment{can we index the indicate there are $S$ groups in the figure?}

@@

Before we start with the case analysis, we first define several clean events and show that the intersection of them happens with high probability. 
\begin{itemize}
\item \textbf{Concentration of the number of arm $a$ pulls in the first level:} 
\swcomment{can we reuse the previous result?}
For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$. For the $s$-th first-level group, define $W_1^{a,s}$ to be the event that the number of arm $a$ pulls in the $s$-th first-level group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,s}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,s}W_1^{a,s}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S}{T^2}.
\]
\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}
\swcomment{reusable?}
For each first-level group and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in this group pull arm $a$. For the $s$-th first-level group and arm $a$, define $W_2^{s,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{2\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_2^{s,a,t_1,t_2}] \geq 1 - 2\exp(-4\log(T)) \geq 1- 2/T^4.
\]
